%-------------------------
% Resume in Latex
% Author : Mrinmay Dhar
% Template : Jake's Resume Template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Mrinmay Dhar} \\ \vspace{1pt}
    \small +91-8375944027 $|$ 
    \href{mailto:contact@mrinmaydhar.com}{contact@mrinmaydhar.com} $|$ 
    \href{https://www.linkedin.com/in/mrinmaydhar/}{LinkedIn} $|$
    \href{https://github.com/mrinmaydhar}{GitHub}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amity University}{Noida, UP}
      {Bachelor of Technology in Computer Science and Engineering}{2016 -- 2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{Feb. 2026 -- Present}
      {Icertis Solutions Pvt. Ltd.}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Performed migration of customers to \textbf{Multi-Tenant}, eliminating cross-team dependencies and achieving \textbf{TTV} for platform upgrades \textbf{before schedule}.}
        \resumeItem{Implemented \textbf{APIM} for API reporting data. Data helped to optimize downstream application and \textbf{reduce failure rates from 25\% to 0.01\%} after collaborating with client engineering teams.}
        \resumeItem{Engineered an \textbf{event-driven orchestration} layer on APIM. Implemented batch processing and optimized payload size via query filtering, \textbf{reducing monthly call volume by over 90\%} (120k to $\sim$10k).}
        \resumeItem{Migrated the business API layer and DocuSign integrations from legacy token-based authentication to \textbf{OAuth 2.0}. This implemented a \textbf{robust security layer} for connecting downstream and internal applications.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July 2023 -- Feb. 2026}
      {Icertis Solutions Pvt. Ltd.}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Worked on multiple defects and tech debts requiring extensive \textbf{code refactoring} and several PBIs to upgrade customer customizations, resulting in \textbf{zero bugs} during UAT and hyper-care phases.}
        \resumeItem{Successfully deployed several integrations (\textbf{DocuSign, OAuth, SSO}) for all applicable environments. Developed internal tools to debug issues with deployments.}
        \resumeItem{Rapidly delivered \textbf{POCs and resolved critical bugs} after being brought onto various projects during their cut-over phase.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Associate Software Engineer}{Dec. 2021 -- July 2023}
      {Icertis Solutions Pvt. Ltd.}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Successfully led and deployed \textbf{MS Teams integration} with customers, debugging multiple integration issues and collaborating with stakeholders over several time-zones.}
        \resumeItem{Developed platform customization for multiple partner projects, satisfying business requirements \textbf{months ahead} of the core platform's sprint.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{ALM Workbench} $|$ \emph{Tooling for internal VS extension.}}{\emph{Icertis}}
          \resumeItemListStart
            \resumeItem{{\underline{Configuration Deployment Tool}} - Created a tool that \textbf{automatically updates configuration files} in blob storage, which is referred by hooks used in C\# and TS code.}
            \resumeItem{{\underline{DocuSign Validation Tool}} - Built an \textbf{automated validation system for DocuSign integrations} that verifies configuration like RSA keys/Client IDs and executes required API sequences for P2P.}
            \resumeItem{{\underline{Solution Minification Tool}} - Developed a plugin that compresses project solution and strips NuGet dependencies for static analysis, \textbf{reducing artifact size by 99\%} ($\sim$2GB to $\sim$5MB).}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{oci-home-cloud} $|$ \emph{Cloud infrastructure setup for protecting home network.}}{\href{https://github.com/mrinmaydhar/oci-home-cloud}{\emph{GitHub}}}
          \resumeItemListStart
            \resumeItem{VPS on OCI that acts as exit node, routing network traffic through \textbf{Wireguard VPN}.}
            \resumeItem{Network devices are protected by \textbf{Cloudflare tunnels}, \textbf{Crowdsec}, and \textbf{UFW}.}
            \resumeItem{\textbf{Traefik} is configured as reverse proxy to provide FQDNs to internal services.}
            \resumeItem{VM is provisioned via \textbf{Terraform} plans and managed by \textbf{Ansible} to ensure reproducibility.}
            \resumeItem{All hosted applications are configured via \textbf{Docker Compose} files.}
            \resumeItem{Network fail-over achieved via \textbf{OpenWRT} package - mwan3.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, TypeScript, SQL, PowerShell, Bash} \\
     \textbf{Technologies}{: ASP.NET, HTML, CSS, jQuery, Elasticsearch, ADO, Git, IIS, Swagger, Postman} \\
     \textbf{Infrastructure \& Tools}{: Agile, CI/CD, DevOps, MVC, Linux, REST API, Azure}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
